Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-01 analysis/sim/run_simpw.Rmd
try dose
sims

library("tidyverse")
library("parallel")
library("edgeR")
library("DESeq2")
library("limma")
library("stringi")
library("kableExtra")
source("simpw_func.R")

@@

@@

```{r,getcounts}

a<-countData()

@@

gsets<-randomGeneSets(a,setsize=50,nsets=500)

@@

SIMS=16
FRAC_DE=0.05
FC=1
N_REPS=4
DGE_FUNC="deseq2"
SUM_COUNT=3e7
VARIANCE=c(0.25,0.3,0.35,0.4,0.45)

@@

>>>>

#library("tidyverse")
library("parallel")
library("edgeR")
library("DESeq2")
library("limma")
library("stringi")
library("kableExtra")
library("fgsea")
library("clusterProfiler")
source("simpw_func.R")

@@

xxx object slots

1. expression counts

2. ground truth up genes

3. ground truth down genes

4. ground truth up gene sets

5. ground truth down gene sets

6. DE result (DESeq2)

7. DE genes up observed

8. DE genes down observed

9. fgsea up gene sets

10. fgsea down gene sets

11. phyper up gene sets

12. phyper down gene sets

13. clusterprofiler_default up gene sets

14. clusterprofiler_default down gene sets

15. clusterprofiler_fixed up gene sets

16. clusterprofiler_fixed down gene sets

17. clusterprofiler_nobg up gene sets

18. clusterprofiler_nobg down gene sets

19. fisher up gene sets

20. fisher down gene sets

21. DOSE up gene sets

22. DOSE down gene sets

@@

```{r,getcounts,warning=FALSE}

a <- countData()

@@

gsets <- randomGeneSets(a,setsize=20,nsets=200)

@@

SIMS=8
FRAC_DE=0.05
FC=1
N_REPS=5
DGE_FUNC="deseq2"
SUM_COUNT=3e7
VARIANCE=c(0.3,0.35,0.4)

@@

res <- do.call(rbind,res)
